---
title: "XML"
author: "JP"
date: "5/30/2019"
output: html_document
---

XML is `markup` (describing the structure) and `content` (the data).

Most `markup` is in the form of `tags` of the form `<tagname>... </tagname>`

An XML `element` spans from a start tag to an end tag. 

in `<title>A New Hope</title>` "A New Hope" is the `content` between the "title" `tags`.

XML elements can be described as parents, siblings and children based on their hierarchical relationships. 

```{r}
pacman::p_load(xml2)
```

```{r}
# Get XML revision history
resp_xml <- rev_history("Hadley Wickham", format = "xml")

# Check response is XML 
http_type(resp_xml)

# Examine returned text with content()
rev_text <- content(resp_xml, as = "text")
rev_text

# Turn rev_text into an XML document
rev_xml <- read_xml(rev_text)

# Examine the structure of rev_xml w/o data
xml_structure(rev_xml)
```

# XPATHS
allow you to specify nodes in an XML document
```{r}
movies_xml <- read_xml('<?xml version="1.0" encoding="UTF-8"?>
<movies>
  <title>"Star Wars"</title>
  <movie episode = "IV">
    <title>A New Hope</title>
    <year>1977</year>
  </movie>
  <movie episode = "V">
    <title>The Empire Strikes Back</title>
    <year>1980</year>
  </movie>
</movies>')
```

`/` - to find elements with tag node at this level
```{r}
xml_find_all(movies_xml, xpath = "/movies/movie/title")
```

`//` - find nodes at any level below
```{r}
xml_find_all(movies_xml, "//title")
```

Note that above code also returns "Star Wars" which is higher level data than we probably want.

`@` - to extract `attributes` within another node, e.g., episodes within movies. 
```{r}
xml_find_all(movies_xml, "//movie/@episode")
```

Get nodes with `xml_find_all()`
Extract contents with `xml_text`, `xml_double()`, `xml_integer()` or `as_list()`

```{r}
# All rev nodes
rev_nodes <- xml_find_all(rev_xml, "//rev")

# The first rev node
first_rev_node <- xml_find_first(rev_xml, "//rev") #xml_find_first() works like xml_find_all() but only extracts first node found

# Find all attributes with xml_attrs()
xml_attrs(first_rev_node)

# Find user attribute with xml_attr()
xml_attr(first_rev_node, attr = "user")

# Find user attribute for all rev nodes
xml_attr(rev_nodes, ns = "rev", attr = "user")

# Find anon attribute for all rev nodes
xml_attr(rev_nodes, ns = "rev", attr = "anon")
```

```{r get_revision_history}
get_revision_history <- function(article_title){
  # Get raw revision response
  rev_resp <- rev_history(article_title, format = "xml")
  
  # Turn the content() of rev_resp into XML
  rev_xml <- read_xml(content(rev_resp, "text"))
  
  # Find revision nodes
  rev_nodes <- xml_find_all(rev_xml, "//rev")

  # Parse out usernames
  user <- xml_attr(rev_nodes, "user")
  
  # Parse out timestamps
  timestamp <- readr::parse_datetime(xml_attr(rev_nodes, "timestamp"))
  
  # Parse out content
  content <- xml_text(rev_nodes)
  
  # Return data frame 
  data.frame(user = user,
    timestamp = timestamp,
    content = substr(content, 1, 40))
}

# Call function for "Hadley Wickham"
get_revision_history("Hadley Wickham")
```

